%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%% https://www.ctan.org/pkg/moderncv?lang=en

\documentclass[10pt,a4paper,roman]{moderncv}
% possible options include font size ('10pt', '11pt' and '12pt'),
%% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and 
%% font family ('sans' and 'roman')


\moderncvstyle{casual}                             % style options are 'casual'
                                                    % (default), 'classic', 'oldstyle' and
                                                    % 'banking'
%% Choosing color
\moderncvcolor{black}                               % color options 'blue' (default),
                                                  % 'orange', 'green', 'red', 'purple',
                                                  % 'grey' and 'black'

%% Another Options for colours
% \moderncvtheme[green]{classic}                % idem
% \definecolor{color0}{rgb}{0,0,0}% black
% \definecolor{color1}{rgb}{0.38,0.69,0.19}% green
% \definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey




\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
% [REF] http://tex.stackexchange.com/questions/588/how-can-i-change-the-margins-for-only-part-of-the-text

\usepackage{xstring}
\def\FormatName#1{%
  \IfSubStr{#1}{Xochicale}{\textbf{#1}}{#1}%
}
% Using my_unsrt.bst
% [REF] http://tex.stackexchange.com/questions/33330/make-one-authors-name-bold-every-time-it-shows-up-in-the-bibliography


\usepackage[scale=0.85]{geometry}% adjust the page margins
\setlength{\hintscolumnwidth}{37mm} %
%  if you want to change the width of the column with the dates


\usepackage{multibib}
\newcites{pr}{Peer-Reviewed}
\newcites{npr}{Non-Peer Reviewed}
\newcites{pp}{Preprints}




%\setlength{\makecvtitlenamewidth}{10cm} % for the 'classic' style, if you want to force
%the width allocated to your name and avoid line breaks. be careful though, the length is
%normally calculated to avoid any overlap with your personal info; use this at your own
%typographical risks...



\name{Miguel}{Xochicale}
\title{Curriculum Vitae -- September 2020}
\renewcommand*{\namefont}{\fontsize{30}{40}\mdseries\upshape}

% \quote{
%
% } % optional, remove / comment the line if not wanted


%----------------------------------------------------------------------------------
%            content
%
\begin{document}


%-----       resume       ---------------------------------------------------------
%
%
\makecvtitle



% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \cvline{Scientific Focus}{\small \textbf{Human-Humanoid Imitation}:
%     human-humanoid interaction; nonlinear dynamics.}
% \cvline{Keywords}{\textbf{Human-Robot Interaction}, \textbf{Wearable Inertial Sensors}, \textbf{Human-Activity Recognition},  \textbf{Deep Learning}.}
%


\vspace{-10mm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%
\section{Personal Details \& Contact}
%
% For more icons
% http://mirror.ox.ac.uk/sites/ctan.org/fonts/fontawesome/doc/fontawesome.pdf

\begin{changemargin}{2.4cm}{0.5cm}
  \begin{minipage}{.4\textwidth}
    \begin{description}
	\item[Full name] Miguel Angel P\'erez Xochicale
     	\item[Date of birth] 29-09-1981
	\item[Citizenship] Mexican 
	\item[\faMobile ]  (+44) 0744 281 7616 (UK)
	\item[Email]  
		\href{miguel.xochicale@kcl.ac.uk}
			{miguel.xochicale@kcl.ac.uk}

     \end{description}
  \end{minipage}
  \begin{minipage}{.4\textwidth}
  \begin{description}
     	\item[\faHome]  \href{http://mxochicale.github.io}{http://mxochicale.github.io}
	\item[\faTwitter ] \href{https://twitter.com/_mxochicale}{@\textunderscore mxochicale}
	\item[\faGithub]  \href{https://github.com/mxochicale}{@mxochicale}
	%\item[\faLinkedin]
	\item[ORCID:] \href{http://orcid.org/0000-0002-8225-7517}{0000-0002-8225-7517}
   \end{description}
  \end{minipage}
\end{changemargin}
% \vspace{10pt}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%
\section{Personal statement}

\begin{changemargin}{2.4cm}{0.5cm}
I have passion for Robotics, Chaos, AI, Brains and Open Science.
I am currently pushing forward the state-of-the-art of 
ultrasound-guided procedures by making scientific contributions 
to new algorithms, software and hardware.
I have 21 years' experience in human-robot interaction, 
electronics, mechatronics and signal processing, along 
with 13 years' experience as a teaching assistant in 
Mechatronic and Computer Engineering. 
\end{changemargin}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%
\section{Education}
\cventry{11/2014 -- 11/2018}{Ph.D. in Computer Engineering}{University of Birmingham}{UK}{}
  {Thesis: Nonlinear Analysis to Quantify Movement Variability in Human-Humanoid Interaction.
% \href{https://doi.org/10.5281/zenodo.1473140}{\faFilePdfO}
% \href{https://github.com/mxochicale/phd-thesis}{\faGithubAlt}
% \href{https://github.com/mxochicale/phd-thesis-code-data}{\faCode}
	\\ Supervisors: Professor Chris Baber and  Professor Martin Russell
	\\ Thesis submission: 26/10/2018. Passed Viva: 11/01/2019. 
	Awarded PhD degree: 12/07/2019. \\
I published the first Open Access and 100\% 
reproducible PhD Thesis since the establishment of 
University of Birmingham in 1900.  
Thesis: \href{https://doi.org/10.5281/zenodo.3384145}{\faFilePdfO}
Github: \href{http://doi.org/10.5281/zenodo.3384281}{\faGithubAlt}
Website: \href{https://mxochicale-phd.github.io/site/}{\faExternalLink}
}

\cventry{09/2004 -- 09/2006}{M.Sc. in Signal Processing}
  {Institute of Astrophysics, Optics and Electronics}{M\'exico}{}
  {Thesis: Digital Filter FIR with less multipliers
  \href{https://github.com/mxochicale/publications/blob/master/thesis/M.Sc./doc/MPXochicale_MScThesis-2016.pdf}{\faFilePdfO}
  \href{https://github.com/mxochicale/publications/tree/master/thesis/M.Sc.}{\faGithubAlt}
  \\ Supervisor: Dr. Gordana Jovanovic Dolecek}

\cventry{08/1999 -- 09/2004}{B.Eng. in Electronics}{Puebla Institute of Technology}{M\'exico}{}
  {Thesis: Speed control for a two-degrees-of-freedom Robot in LabVIEW.
  \href{https://github.com/mxochicale/publications/blob/master/thesis/B.Eng./doc/MPXochicale_BachelorEngThesis-2003.pdf}{\faFilePdfO}
  \href{https://github.com/mxochicale/publications/tree/master/thesis/B.Eng.}{\faGithubAlt}
  \\ Supervisor: M.Sc. Jos\'e Esteban Torres Le\'on.}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%
\section{Professional Experience}

\cventry{04/2019 -- present}{Research Associate in Software and Hardware Engineering}{King's College London}{}{}
{Achievements:
In the context of Ultrasound Needle Tracking,
I am developing validation experiments with linear stages under Windows and GNU/Linux OS, 
%new algorithms using image entropy, 
designing electronic PCBs, 
characterising ultrasonic transducers, 
and contributing to real-time tracking software based on Python language
via GitHub. All the previous activities in collaboration with an amazing 
team of renowned clinicians, engineers and researchers in KCL and UCL.
Additionally, I am leading the preparation of two manuscripts.
}


\cventry{02/2013 -- 08/2013}{Research Assistant in Robotics}{INAOE's Robotics Laboratory}{M\'exico}{}
{Achievements: I developed a Human-Robot Interaction Demo for dancing activities based on 
a Patrolbot mobile robot and a ZSTAR3 Radio Frequency single three-axial accelerometer.
%For the demo, I explored four hand gestures where the user worn the accelerometer at his/her 
%left wrist in order to create simple dance activities with the mobile robot. 
\href{https://sites.google.com/site/perezxochicale/projects/demodance}{(Documents and code: \faExternalLink)}.
}

\cventry{01/2012 -- 01/2013}{Lecturer in Mechatronic Engineering}
{Universidad Madero}{Puebla, M\'exico}{}
{Achievements:
I proposed and supervised the following students' projects: Haptic Referee Glove,
 Lightmetre and Pychometre Sensors, Smart Irrigation, Persistent Of Vision Bicycle Wheel
 and a Delta Robot Structure 
\href{https://sites.google.com/site/perezxochicaleprojects/studentprojects}{(see documentation and code: \faExternalLink)}.
Additionally, I proposed and designed a Mechatronic Laboratory which includes: 
(i) a benchmark for laboratories in mechatronics in M\'exico and Puebla, 
(ii) a 3D layout design and 
(iii) minimal requirements of hardware and software for the laboratory
 \href{https://sites.google.com/site/perezxochicaleprojects/mechatronicslaboratorydesign}{(see documentation and layout: \faExternalLink)}.
}

\cventry{09/2003 -- 03/2004}{Research Internship in Robotics}
{INAOE}{M\'exico}{}
{Achievements:
I implemented a speed control for a two-degree-of-freedom robot with microcontrollers
PIC 16F84 and 16F877 that made communication via RS-232 using Virtual Instruments on LabVIEW.
}


\vspace{20mm}

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%
\section{Open Access Publications (OA).
	\href{http://orcid.org/0000-0002-8225-7517}{ [ORCID ID: 0000-0002-8225-7517 \faExternalLink]}
	}
\bibliographystylepr{plain}
\bibliographypr{peer-reviewed}

\bibliographystylepp{plain}
\bibliographypp{preprints}

\bibliographystylenpr{plain}
\bibliographynpr{non-peer-reviewed}

%%%\citepr{MPXochicale_HAI2017,MPXochicale_HRI2017,mxochicale2016_werob,mxochicale2006_ced,mxochicale2016_derdis}
%\citepr{MPXochicale_HAI2017,MPXochicale_HRI2017,mxochicale2016_werob,mxochicale2016_derdis}
%\citenpr{MXochicale_RRTS2020, MXochicale_ICDEA2019, MXochicale_SMLDS2019, MXochicale_ECCC2018, MXochicale_CERE2018}
%\citepp{mxochicale2018arXiv}

%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%
\section{Teaching Experience}

\cventry{01/2020--04/2020}{Teaching Associate}
{King's College London}{UK}{}
{
(01/2020--04/2020) Medical Robotics. Lecturer: Christos Bergeles
}



\cventry{08/2014--04/2018}{Teaching Associate}
{University of Birmingham}{UK}{}
{
(01/2018--04/2018) Engineering Maths 2. Lecturers: Professor Martin Russell, Dr Carl Anthony \\
(08/2017--12/2017) Engineering Maths 2. Lecturer: Professor Martin Russell \\
(08/2017--12/2017) Computing for Engineering. Lecturer: Dr Sridhar Pammu \\
(01/2017--04/2017) Matlab Laboratories. Lecturer: Dr Edward Tarte \\
(08/2016--12/2016) Computing for Engineering. Lecturer: Dr Sridhar Pammu \\
(08/2014--12/2014) Small Embedded Systems. Lecturer: Professor Chris Baber
}

\cventry{08/2013--12/2013}{Teaching Associate}
{Bilingual Hight School TECMilenio University}{Puebla, M\'exico}{}
{
Information Technology \href{https://sites.google.com/site/perezxochicale/teaching/iit}{\faExternalLink},
Euclidian Geometry  \href{https://sites.google.com/site/perezxochicale/teaching/euclidean-geometry}{\faExternalLink}
and
Microsoft Office Access \href{https://sites.google.com/site/perezxochicale/teaching/moa}{\faExternalLink}
}

\cventry{2012}{Teaching Associate in Mechatronic Engineering}
{Universidad Madero}{M\'exico}{}
{Fundamentals of Automation
\href{https://sites.google.com/site/perezxochicale/digital-electronics}{\faExternalLink},
Industrial Electronics \href{https://sites.google.com/site/perezxochicale/ie}{\faExternalLink},
Research Projects \href{https://sites.google.com/site/perezxochicale/latex/thesistemplate}{\faExternalLink},
Metrology \href{https://sites.google.com/site/perezxochicale/metrology}{\faExternalLink},
Physics \href{http://goo.gl/fffnG}{\faExternalLink},
Computer Integrating Manufacturing, and Power Electronics
}

\cventry{2007 -- 2012}{Teaching Associate in Electronic Engineering}
{Universidad Iberoamericana Puebla}{M\'exico}{}
{Stochastic Processes 
\href{https://sites.google.com/site/perezxochicale/stochastic-processes-course}{\faExternalLink},
Digital Signal Processing
\href{https://sites.google.com/site/perezxochicale/digital-signal-processing-course}{\faExternalLink}
and Analog Filters.
}

\cventry{08/2006 -- 06/2007}{Teaching Associate in Mechatronic Engineering}
{Instituto Tecnol\'ogico Superior de Atlixco}{M\'exico}{}
{
(January-June 2007.) Electronics I, Numerical Methods, and Electricity and Magnetism. \\ 
(August-December 2006) Electricity and Magnetism, and Electricity and Industrial Electronics 
}



\vspace{20mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%
\section{Technical Skills}
\cvitem{General}{
GNU/Linux Operating System user (e.g. OpenSuse, Debian and Ubuntu)[2005-present]
Single-board computers and microcontrollers (e.g. 
NVIDIA Jetson Nano, RaspberryPi, BeagleBone, Arduino and PIC)[2010-present],
Inertial Measurement Units (e.g. calibration, collection and data analysis)[2013-present], 
Graphic design (e.g. Inkscape, GIMP)[2014-present],
Web design (e.g. Github pages, Jekyll)[2015-present], and
Artificial Neural Networks (e.g. TensorFlow and PyTorch)[2017-present].
}
\cvitem{Programming}{
Python[2014-present],
R[2013-present], 
Robot Operating System (ROS)[2016-present],
GNU-Octave (or MatLab)[2009-present],
\LaTeX [2006-present], 
C and C++[2015-present],
Processing[2012-present], 
the shell[2010-present], 
GNU-emacs[2010-present],
vim[2016-present], 
pandoc[2017-present],
open-source enthusiast at GitHub (\href{https://github.com/mxochicale}{@mxochicale})[2015-present], and
learning continuous integration and continuous delivery [2019-present]. 
}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%
\section{Awards and Honours}

\cvitem{11/01/2017}{
My work ``Towards Healthy Ageing with Humanoid Robots'' was selected 
for a talk at the second forum of Mexican Talent, Innovation Match MX 2017,
\href{https://github.com/mxochicale/InnovationMatchMX/tree/master/2017}{\faExternalLink}
\href{https://github.com/mxochicale/InnovationMatchMX/blob/master/2017/presentation/IMMX-MA-0058.pdf}{\faFilePdfO}
\href{https://www.youtube.com/watch?v=wNWzpdXdm5U}{\faYoutube}
}

\cvitem{16-18/06/2016}{
I won the best poster award at
the XIV Symposium of Mexican Students in the UK at University of Edinburgh.
\href{https://github.com/mxochicale/symposiummx/tree/master/2016}{\faExternalLink}}

\cvitem{20-24/07/2015}{My project of a low-cost robot was selected among 125 applications received from 35 countries
and presented at the first international public entrepreneurship program in Mexico (MECATE 2015).
\href{http://let-emprendimientopublico.mx/en/portfolio_category/mecate-primera-generacion-en/}{\faExternalLink}
\href{https://www.youtube.com/watch?v=VjVGnwD422g}{\faYoutube}}

\cvitem{11/2014-11/2018}{
Ph.D. scholarship by the Mexican National Council on Science and Technology.}

\cvitem{25-27/05/2013}{
Markovito's team  won the first place at the Mexican Tournament of Robotics 2013 in the category at HOME
where I presented a Human-Robot Interaction Dance Demo. \href{https://www.youtube.com/watch?v=Kw-lZam_qZI}{\faYoutube}}

\cvitem{09/2004-09/2006}{
M.Sc. scholarship by the Mexican National Council on Science and Technology.}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extra Activities}




\cventry{04-2019 -- present}
{Outreach activities and scientific engagement}
{King's College London, UK}
{}
{}
{
(02-2020 -- 06-2020) Alexandra Lautarescu and I are organising 
the Reproducible, Interpretable, Open, \& Transparent Science Club
at St Thomas' Hospital \\
(20-08-2019) In2ScienceUK: sharing my scientific journey to young
scientist on how they can become better scientist. \\
(09-2019) New Scientist Live: showcasing software segmentation
that helps doctors to create 3D models of brain tumors using AI.
}
{}







\cventry{2013 -- present}
{Founder of LibrE Robotics}
{a non-profit organization aiming to freely transfer 
knowledge in Robotics to Mexican children}
{GitHub: \href{https://github.com/librerobotics}{\faGithubAlt} }
{Website: \href{https://sites.google.com/site/LibreRobotics/}{\faExternalLink}}
{(2019--present) Artificial Intelligence and Robotics for Children (air4children) 
GitHub: \href{https://github.com/librerobotics/air4children}{\faGithubAlt}
Slides: \href{https://github.com/librerobotics/air4children/blob/master/docs/slides/presentation.air4children.pdf}{\faFilePdfO} 
}
{}  



\cventry{2017 -- 2018}
{Developer of Machine Learning for Mexico}
{}
{GitHub: \href{https://github.com/ML4MX}{\faGithubAlt} }
{Website: \href{https://ml4mx.github.io/website/}{\faExternalLink}}
{}  % arguments 3 to 6 are optional



\cventry{08/2014 -- 06/2018}
{Outreach activities and scientific engagement}
{University of Birmingham, UK}
{}{}
{
(05-2018) Finalist at the Three Minute Thesis Competition 2018.
Video: \href{https://www.youtube.com/watch?v=07ewRYcS-0g}{\faYoutube} and 
GitHub: \href{https://github.com/mxochicale/3mt}{\faGithubAlt}. \\  
(2015--2018) Research Poster Conference for 
(2015) \href{https://github.com/mxochicale/PhD/blob/master/posters/Research_Poster_Conference_UoB/2015/poster/poster.pdf}{\faImage}, 
(2016) \href{https://github.com/mxochicale/PhD/blob/master/posters/Research_Poster_Conference_UoB/2016/poster/poster.pdf}{\faImage}, and  
(2018) \href{https://github.com/mxochicale/PhD/blob/master/posters/Research_Poster_Conference_UoB/2018/poster/main/map479-poster-uob2018.pdf}{\faImage}.
GitHub: \href{https://github.com/mxochicale/PhD/tree/master/posters/Research_Poster_Conference_UoB}{\faGithubAlt}. \\
(2014--2018) Presenting Demos of Human-Robot Interaction at the Undergraduate Open Days.
GitHub: \href{https://github.com/mxochicale/opendayuob-hridemo}{\faGithubAlt}. \\ 
(2017--2018) Coordinator of the Science Seminars for the Mexican Society. 
GitHub: \href{https://github.com/MexicanSocietyUoB}{\faGithubAlt}, 
Website: \href{https://mexicansocietyuob.github.io/seminars/}{\faExternalLink}. \\ 
}




%\cventry{2014-2018}
%{Outreach Activities: How to build low-cost robots for children}
%{}
%{at University of Birmingham, UK} 
%{GitHub: \href{https://github.com/librerobotics/printable-robots}{\faGithubAlt} }
%{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%
%%%%
%\section{Languages}
%\cvitemwithcomment{Spanish}{Native}{}
%\cvitemwithcomment{English}{Fluent}{}
%%\cvitemwithcomment{English}{Fluent}{IETLS Band Score 6.0, January 2014}
%


\end{document}
